Incremental Forward Reasoning for White-Box~Proof~Search

### 2025-02-17 paper.tex
Add lazy insertion optimisation in implementation and remove indexing

\paragraph{Indexing.}
When adding a hypothesis $h : T$ to the partial match state, we add it to the rule state of each rule $r$ such that $h$ matches a slot of $r$.
To optimise this operation, we use an imperfect discrimination tree index that, for each rule $r$ with slot $i$ corresponding to a premise of type $Tᵢ$, maps the type $Tᵢ$ to the pair $(r, i)$.
Querying this index for $T$ quickly determines all rules and slots for which $h$ is likely relevant.

>>>>

\paragraph{Lazy Insertion.}
Adding a hypothesis to a rule state is fairly cheap, but not free: it involves one unification for each premise that the hypothesis likely matches (according to a discrimination tree index), followed by several operations on the variable indices.
We therefore delay insertions until the index has selected at least one hypothesis for each slot.
This helps, for example, with the definitional rule for involutive functions: if $f : α → α$ is involutive, then for any $a : α$ we have $f (f a) = a$.
When used as a forward rule, the premise $a$ matches any non-propositional hypothesis, but this is only relevant if there is, in fact, an involutive function is the context.
